---
title: 'Problem Set Five'
author: 'Riley Roach'
output: word_document
---

``` {r echo=TRUE}
library(tidyverse)
library(olsrr)
meapsingle<-
   read.csv('meapsingle.csv')
str(meapsingle)
```
#Part I
```{r}
attach(meapsingle)
q_one_model<-
   lm(math4~pctsgle,
      meapsingle)
summary(q_one_model)
library(tidyverse)
ggplot(meapsingle,
       aes(x=pctsgle,
           y=math4)) +
   geom_smooth()
```
The effect of single parenthood seems rather large.

#Part II
```{r}
q_two_model<-
   lm(math4~pctsgle +
         lmedinc +
         free,
         meapsingle)
summary(q_two_model)
par(mfrow=c(2,2))
plot((lm(pctsgle~lmedinc)))
plot((lm(pctsgle~free)))
ols_coll_diag(q_two_model)
```
The coefficient increases. The reason for this, when looking at the residual plots, is that *free* appears to be multicollinear with *pctsgle*. Also, the VIF of *single* is rather high and needs further investigation.

#Part III
```{r}
q_three_model<-
   lm(lmedinc~free,
      meapsingle)
summary(q_three_model)      
```
This is the sign I expected. The correlation is highly significant, meaning that the two are influential on one another.

#Part IV
Yes, one of the variables should be dropped, although choosing which variable to omit requires further analysis.

#Part V
```{r}
ols_coll_diag(q_two_model)
```
The *pctsgle* variable reports the highest VIF. Also, the tolerance is low, meaning that only a small amount of the collected data can be used for an unbiased model.
This does suggest that a different model should be used. A variable more narrow may provide better analysis.
