---
title: 'Problem Set Six'
author: 'Riley Roach'
output: word_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

``` {r}
load("~/RStudioProjects/School Projects/590hw6/wooldridge/data/k401ksubs.RData")
library(tidyverse)
library(tidytext)
library(texreg)
```
#Part I
```{r}
single_person_households<-
   table(k401ksubs$fsize==1)

single_person_households
```
There are 2017 single-person households.

#Part II
```{r results='asis'}
k401ksubs_single <-
   k401ksubs %>%
   group_by(fsize) %>%
   filter(!(fsize!=1))

model_ii <-
   lm(nettfa ~ inc + age,
      k401ksubs_single)

summary(model_ii)

library(texreg)

htmlreg(list(model_ii),
        stars = c(0.01,
                  0.05,
                  0.10))
```

Age being positively correlated to net financial wealth is interesting given that this population consists of single-person households. This may arrise from single-person households spending less income on items that multi-person households utilize.

#Part III
 
The intercept may suggest the "base" cost of living, with controlling all other variables at 0.

#Part IV

```{r}
summary(model_ii)

p_value_partIV <- 2.2e-16
```

The *p*-value for the test $H_0$ : $B_2$ = 1 against $H_A$ : $B_2$ < 1 is `r p_value_partIV`. We can reject $H_0$ at the 1% significance level.

#Part V
```{r results = 'asis'}
model_v <-
   lm(nettfa ~ inc,
      k401ksubs_single)

htmlreg(list(model_ii,
             model_v),
        stars = c(0.01,
                  0.05,
                  0.10))
```

The coefficient is not different by much. This suggests that income is not prone to influence from other variables that may be considered for the model.

