---
title: "Problem Set 07"
author: "Riley Roach"
output:
    html_document:
      highlight: kate
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)
```

```{r}
load('~/Datasets/wooldridge/data/nbasal.RData')
library(tidyverse)
library(tidytext)
library(texreg)
library(broom)
library(car)
attach(nbasal)
library(car)
library(broom)
```




#Part I

```{r results='asis'}
model_i <-
    lm(points ~
           exper +
           expersq +
           age +
           coll,
       nbasal)
htmlreg(model_i, stars = c(0.01, 0.05, 0.10), star.symbol = "\\*", custom.model.names = "Model 1", caption = "Part (i) Model Results", caption.above = TRUE,
        doctype = FALSE)

```

# Part II
The value of experience decreases the points-per-game at 16 years. This makes sense, since at 16 years of age, players are worn down.
```{r}
results_i <- tidy(model_i)
exper_i <-
    results_i %>%
    filter(term == 'exper') %>%
    select(estimate)
expersq_i <-
    results_i %>%
    filter(term == 'expersq') %>%
    select(estimate)
exper_max <- (-1 * exper_i) / (2 * expersq_i)
exper_max
```
Moreover, a small number would indicate that players have short careers.

#Part III
```{r}
summary(model_i)
```
A possible reason for *coll* having a negative statistically significant coefficient is that players who are likely to be elite in the NBA often enter the NBA before finishing college.

#Part VI
```{r eval = FALSE}
model_vi <-
    lm(points ~
           exper +
           expersq +
           age +
           agesq +
           coll,
       nbasal)
htmlreg(model_vi,
        stars = c(0.01, 0.05, 0.10),
        star.symbol = "\\*",
        custom.model.names = "Model 1",
        caption = "Part (i) Model Results",
        caption.above = TRUE,
        doctype = FALSE)
```
The results suggest that adding a quadratic *age* variable is unnecessary. This is because *coll* and *exper* are influenced by age, as larger *coll*s and *exper*s require the player to have a higher age.

#Part V
```{r}
model_v <-
    lm(lwage ~
           points +
           exper +
           expersq +
           age +
           coll,
       nbasal)

```


#Part VI
```{r}
model_vi_test <-
    linearHypothesis(model_v,
                     c('age = 0',
                       'coll = 0'))
model_vi_test
```

The above test implies that *coll* and *age* are not jointly significant. This implies that the variables, *points*, *exper* and *expersq* have such an influence that age and education are not important here.


